---
output: github_document
---

# From poles to tropics: A multi-biome synthesis investigating the controls on river Si exports

- Primary Investigators: Joanna Carey & Kathi Jo Jankowski
- [Project Summary](https://lternet.edu/working-groups/river-si-exports/)
- [Participant Information](https://www.nceas.ucsb.edu/projects/12816)

## Script Explanations

Scripts in this repository are described below:

- **`wrangle_chemistry.R`** - Ingest chemistry files (per river / stream gage), do necessary harmonizing to meet desired format requirements, and create a single, analysis-ready chemistry dataset

## Repository Content

See below for a "tree" of this repository's content:

```{r pkg-load, include = F}
# Load needed package
# install.packages("supportR")
library(supportR)
```

```{r github-tree, message = F, warning = F}
supportR::github_tree(repo = "https://github.com/lter/lterwg-silica-data", exclude = "docs")
```

## Related Repositories

This working group has several repositories. All are linked and described (briefly) below.

- [lter/**lterwg-silica-data**](https://github.com/lter/lterwg-silica-data) - Primary data wrangling / tidying repository for "master" data files
- [SwampThingPaul/**SiSyn**](https://github.com/SwampThingPaul/SiSyn) - Original repository for this working group. Performs many functions from data wrangling through analysis and figure creation
- [lsethna/**NCEAS_SiSyn_CQ**](https://github.com/lsethna/NCEAS_SiSyn_CQ) - Examples concentration (C) and discharge (Q) relationships for a wide range of solutes
- [lter/**lterwg-silica-spatial**](https://github.com/lter/lterwg-silica-spatial) - Extracts spatial and climatic information from within watershed shapefiles
- [njlyon0/**lter_silica-cryosphere**](https://github.com/njlyon0/lter_silica-cryosphere) - Performs analysis and visualization for the cryosphere manuscript
